Fair Decision Making

### 2023-07-07 Notes/meeting_notes.tex
Added Day 32: notes and blog.

\textit{Led by Bang An.} \\
\end{document}

>>>>

\textit{Led by Bang An.} \\

\section{Source-Free Domain Adaptation}

\textit{Led by Hesun Chen.} \\

Datapoints from different datasets confer different distributions. Distribution Shift

In classic DA, source and target data are referenced at the same time. This cross reference may cause privacy leaks, and so a better way is to keep data local. Furthermore, frequently referencing data results in heavy communication costs. In source-free DA, source and target data are referenced separately (first, models are trained on source domains and then it is passed to the target domain).

Pseudo labeling is important since labeled data becomes inaccessible in later stages. Three types of pseudo label methods include hidden structure based, data augmentation based, and knowledge distillation based.
\end{document}

### 2023-07-07 Notes/paper_notes.tex
Added Day 32: notes and blog.

\begin{approach*}
Many approaches for debiasing Vision-Language Models require training or fine-tuning models using resampled datasets, or modified objectives, which can be computationally expensive. The paper proposes a general approach for "self-debiasing foundation vision-language models by projecting out biased directions in the text embedding." \\

@@

@@

Existing Facial Detection Algorithms are evaluated on the widely known \href{http://shuoyang1213.me/WIDERFACE/index.html}
{WIDER FACE} (Face Detection Benchmark Dataset). A number of Facial Detection Algorithms and their evaluations on WIDER FACE can be found \href{http://shuoyang1213.me/WIDERFACE/WiderFace_Results.html}{here}. Note that some of these algorithms are object detection algorithms adapted for facial recognition, but some are also specifically facial detectors (e.g. RetinaFace, YOLO5Face).

>>>>

\begin{approach*}
Many approaches for debiasing Vision-Language Models require training or fine-tuning models using resampled datasets, or modified objectives, which can be computationally expensive. The paper proposes a general approach for ``self-debiasing foundation vision-language models by projecting out biased directions in the text embedding." \\

@@

\subsection{\href{https://arxiv.org/pdf/2303.07345.pdf}{Erasing Concepts from Diffusion Models}}

\begin{approach*}
``We propose a fine-tuning method that can erase a visual concept from a pre-trained diffusion model, given only the name of the style and using negative guidance as a teacher. Unlike previous methods, our approach can remove concepts
from a diffusion model permanently rather than modifying
the output at the inference time, so it cannot be circumvented
even if a user has access to model weights."
\end{approach*}

\begin{discussion*}
In our work, it could be beneficial to remove the concept of gender or an association of a specific gender to a profession/occupation. For example, we may want to remove the correlation for doctors being predominately male. \\

On the other hand, removing the entire concept of gender may lead to deformed images, however, so we must be careful when thinking about the concept we want to erase.
\end{discussion*}

There are two types of parameters that will be fine-tuned when a concept is to be erased:

\textbf{Cross-attention parameters} serve as a gateway to the prompt and directly depend on the text prompt, while other parameters (such as \textbf{self-attention parameters}) tend to contribute to a visual concept even if the concept is not mentioned in the prompt. \\

Fine-tuning is done on the cross attentions,
ESD-x, when the erasure must be controlled and
specific to the prompt, such as when a named artistic style
should be erased. On the other hand, fine-tuning of the unconditional layers (non-cross-attention modules), ESD-u, occurs when the erasure is required to be independent of the text in the
prompt, such as when the global concept of NSFW nudity
should be erased.

\begin{discussion*}
It seems like if we erase a specific concept like ``firefighters are predominately male," we would want to fine-tune the cross-attention layer ESD-x so as to not affect the general image output. \\

On the other hand, if we are to erase larger-scale concepts like gender, we will need to be careful that this erasure does not interfere with other generated outputs that may not pertain to gender bias.
\end{discussion*}

@@

Existing Facial Detection Algorithms are evaluated on the widely known \href{http://shuoyang1213.me/WIDERFACE/index.html}
{WIDER FACE} (Face Detection Benchmark Dataset). A number of Facial Detection Algorithms and their evaluations on WIDER FACE can be found \href{http://shuoyang1213.me/WIDERFACE/WiderFace_Results.html}{here}. Note that some of these algorithms are object detection algorithms adapted for facial recognition, but some are also specifically facial detectors (e.g. RetinaFace, YOLO5Face). \\

In our project, we use YOLOv8-face, which is an extension of the YOLOv8 object detector fine-tuned on the WIDER FACE dataset.

\section{Presentation Notes}

\noindent
Let $C_i$ be the confidence the $i^{\text{th}}$ person (in a batch of images or in a single image) is male. \\

\begin{definition}[Fairness Loss]\noindent The \textbf{fairness loss} is \[ \left( \frac{\sum\limits_i C_i}{\text{\# people}} - 0.5 \right)^2.\]
\textit{The goal of this ``loss" is to get the average probability a person is male to be around 0.5, which mitigates the gender bias.}
\end{definition}

\begin{definition}[Confidence Loss]
\noindent The \textbf{confidence loss} is \[ \frac{\alpha}{\text{\# people}} \sum_i -(C_i - 0.5)^2.\]
\textit{The goal of this ``loss" is to get individuals to be distinctly male or female.}
\end{definition}
